# (PART\*) Getting Started {-}

# PIs and Lab Managers

## Introduction

### Who is this guide for?

### What's in this guide?

### Philosophy

## Account Setup

### Overview

This guide provides an opinionated walkthrough on how to set up AnVIL for your lab, based on experiences from many labs actively using AnVIL.  Following our recommendations will help you configure your team so that you can more clearly see where charges are coming from and have greater control over which users can spend your money and access your data.

#### Goals for this guide

```{r, echo=FALSE, fig.alt="List of goals for this guide: 1) get your accounts, 2) set up billing, 3) set up your lab members to do research on AnVIL, and 4) monitor and manage spending."}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd5c49c5c55_0_165")
```

#### Overview of Account Setup

AnVIL uses [Terra](https://anvil.terra.bio/) to run analyses.  Terra operates on Google Cloud Platform, so you’ll pay for all storage and analysis costs through a Google account linked to Terra.  The costs are the standard Google Cloud Platform fees for storing and moving data as well as executing an analysis.  These costs are passed along through Terra without any markup.

```{r, echo=FALSE, fig.alt="Diagram outlining the roles of Google and Terra for AnVIL.  A 'PI' signs in with a Google ID, which lets them create a Google Billing Account.  Money flows from the Google Billing Account to a Terra Billing Project, and then to individual Terra Workspaces"}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_138")
```

1. Create a Google account
1. Set up Google Billing (and claim your free credits!).
    + Add an administrator or viewer (optional)
1. Link Terra to the Google Billing Account
1. Create Terra Billing Projects
1. Set budgets and alerts (optional, but highly recommended)
1. Add users and Workspaces

#### Lab Management Roles

While there are many ways to configure your lab, this guide defines the following roles and responsibilities:

- **PI** - The PI sets up the lab’s Google Cloud Account, creates its Google Billing Account(s), and Google Payment Method(s), links Terra with GCP, and invites Lab Managers to be Google Cloud “Billing Account Users.”

- **Lab Manager** (Optional) - A Lab Manager creates or clones Terra Workspaces and manages who can use those Workspaces. The Lab Manager is also responsible for creating one or more Terra Billing Projects configuring GCP budgets and alerts.  Importantly, **lab managers control who can spend lab money** and should have an understanding of Google Cloud Billing and Terra Billing Projects.  Depending on your lab, the PI may choose to be the only Lab Manager, or may appoint trusted lab members to assist.

- **Data Analyst** - A lab member who is granted write + can-compute access on one or more Terra Workspaces by a Lab Manager and who will run analyses in Terra.  Data Analysts cannot share Terra Workspaces (this prevents them from enabling others to spend lab money).

#### Before you start

- You will need a **credit card or bank account** to activate your free trial and get started.  Don't worry! **You won't be billed until you explicitly turn on automatic billing**, but payment information is needed for verification purposes.
- Before setting up billing yourself, you may want to check with your institutional procurement office and see if they have a preferred account set-up method with Google (such as a third party reseller or an existing account).
- To add lab members, you will need to know the Google account they will use to access Terra.  You can complete most setup steps without this information and then add them once you know the correct accounts.


### Step 1: Create a Google Account

```{r, echo=FALSE, fig.alt="Diagram showing an overview of the six steps. Step 1 is highlighted."}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd5c49c5c55_0_160")
```


Terra operates on Google Cloud Platform, so you will need a (free) Google account which will allow you to

- Access the Terra platform to manage team members, data, and analyses
- Access Google Cloud Platform to manage billing
- Receive alerts when spending reaches specified thresholds

```{r, child=c("reusable_content/_create_google_account.Rmd")}

```

### Step 2: Set up Google Billing

```{r, echo=FALSE, fig.alt="Diagram showing an overview of the six steps. Step 2 is highlighted."}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd5c49c5c55_0_170")
```

Terra operates on Google Cloud Platform, and does not charge any markup.  Rather than paying Terra or AnVIL, users set up billing directly with Google Cloud Platform.

**Make sure to use the same Google account ID you use to log into Terra for Google Cloud Billing.**

To set up billing, you must first create a **Google “Billing Account”**.
You can create multiple Billing Accounts associated with your Google ID.  We recommend creating separate Billing Accounts for different funding sources.

#### Create a Google Billing Account

1. Log in to the [Google Cloud Platform](https://console.cloud.google.com/) console using your Google ID.
    + **Make sure to use the same Google account ID you use to log into Terra.**
1. If you are a first time user, don’t forget to claim your free credits!
    + If you haven't been to the console before, once you accept the Terms of Service you will be greeted with an invitation to "Try for Free."
    +
```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console with the "Try for Free" button highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd5c49c5c55_0_152")
```
    + Follow the instructions to sign up for a Billing Account and get your credits.
        + Choose “Individual Account”.  This “billing account” is just for managing billing, so you don’t need to be able to add your lab members.
        + You will need to give either a credit card or bank account for security. Don't worry! **You won't be billed until you explicitly turn on automatic billing**.
        +
```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Billing Account Setup, with "Individual Account" highlighted.  Also highlighted is text stating "You won\'t be charged unless you manually upgrade to a paid account."'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_145")
```

1. You can view and edit your new Billing Account, by selecting “Billing” from the left-hand menu, or going direction to the billing console [console.cloud.google.com/billing](https://console.cloud.google.com/billing) 
    +
```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console dropdown menu, with "Billing" highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_153")
```
    + Clicking on the Billing Account name will allow you to manage the account, including accessing reports, setting alerts, and managing payments and billing.  We will cover account management in greater detail below.
    +
```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console Billing Page, with the name of the new billing account highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_160")
```

At any point, you can create additional Billing Accounts using the **Create Account** button.  We recommend creating a new Billing Account for each funding source.


#### Add users or viewers (optional)

If you have a project manager or finance administrator who needs access to a Billing Account, you can add them with a few different levels of permissions.  Generally the most useful are:

- **Users** have a great deal of power over spending - they can create new "Billing Projects" and control who can spend money on those projects.  If you have a lab or accounts manager responsible for expenses, it may make sense to add them as a Billing Account User.  If you wish to retain full control over who can spend money on GCP, you should not add any Users.
- **Viewers** can see the activity in the Billing Account but can’t make any changes.  This can be useful for finance staff who need access to the reports, or for lab members to be able to see what their analyses are costing.

Anyone you wish to add to the Billing Account will need their own Google ID.

To add a member to a Billing Project:

1. Log in to the [Google Cloud Platform](https://console.cloud.google.com/) console using your Google ID.
1. Navigate to [Billing](https://console.cloud.google.com/billing)
    +
    ```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console drop-down menu, with "Billing" highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_153")
```
    + You may be automatically directed to view a specific Billing Account.  If you see information about a single account rather than a list of your Billing Accounts, you can get back to the list by clicking "Manage Billing Accounts" from the drop-down menu.
    + 
```{r, echo=FALSE, fig.alt='Screenshot of an individual Google Cloud Billing Account with the drop-down menu item "Manage Billing Accounts" highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_167")
```

1. Check the box next to the Billing Account you wish to add a member to, click "ADD MEMBER".
    +
```{r, echo=FALSE, fig.alt='Screenshot of Google Cloud Billing Accounts Overview. The checkbox next to the name of a Billing Account is checked and highlighted, and the "Add Member" button is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_178")
```

1. Enter their Google ID in the text box. In the drop-down menu, mouse over Billing, then choose the appropriate role.
    +
```{r, echo=FALSE, fig.alt='Screenshot of the dialogue box for adding a member to a Google Cloud Billing Accounts. In the drop-down menu labeled "Select a Role", the item "Billing" and the submenu item "Billing Account Viewer" are highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_185")
```
    
1. Click "SAVE".
    +
```{r, echo=FALSE, fig.alt='Screenshot of the dialogue box for adding a member to a Google Cloud Billing Accounts. The Save button is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_192")
```

### Step 3: Add Terra to the Google Billing Account

```{r, echo=FALSE, fig.alt="Diagram showing an overview of the six steps. Step 3 is highlighted."}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_198")
```

This gives Terra permission to create projects and send charges to the Google Billing Account, and must be done by an administrator of the Google Billing Account.

Terra needs to be added as a "Billing Account User":

1. Log in to the [Google Cloud Platform](https://console.cloud.google.com/) console using your Google ID.
1. Navigate to [Billing](https://console.cloud.google.com/billing)
    +
    ```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console drop-down menu, with "Billing" highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_153")
```
    + You may be automatically directed to view a specific Billing Account.  If you see information about a single account rather than a list of your Billing Accounts, you can get back to the list by clicking "Manage Billing Accounts" from the drop-down menu.
    + 
```{r, echo=FALSE, fig.alt='Screenshot of an individual Google Cloud Billing Account with the drop-down menu item "Manage Billing Accounts" highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_167")
```

1. Check the box next to the Billing Account you wish to add Terra to, click "ADD MEMBER".
    +
```{r, echo=FALSE, fig.alt='Screenshot of Google Cloud Billing Accounts Overview. The checkbox next to the name of a Billing Account is checked and highlighted, and the "Add Member" button is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_178")
```

1. Enter `terra-billing@terra.bio` in the text box.  In the drop-down menu, mouse over Billing, then choose "**Billing Account User**".
    +
```{r, echo=FALSE, fig.alt='Screenshot of the dialogue box for adding a member to a Google Cloud Billing Accounts. The text box is highlighted and has been filled in with "terra-billing@terra.bio".  In the drop-down menu labeled "Select a Role", the item "Billing" and the submenu item "Billing Account User" are highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_203")
```

1. Click "SAVE".
    +
```{r, echo=FALSE, fig.alt='Screenshot of the dialogue box for adding a member to a Google Cloud Billing Accounts. The Save button is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_207")
```

### Step 4: Create Terra Billing Projects

```{r, echo=FALSE, fig.alt="Diagram showing an overview of the six steps. Step 4 is highlighted."}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_217")
```


This is how you enable Terra users to charge to the Google Billing Account.

Note that Google will report charges at the level of Billing Projects.  **If you create only one Billing Project for your lab, you will not be able to see a breakdown of where charges are coming from**.

It is highly recommended that you create separate Billing Projects for each category of spending you would like to track.  For example:

- A Billing Project for each **lab member**, if you would like to track individual spending
- A Billing Project for each **analysis type**, if you would like to track spending on e.g. RNA-seq vs. variant calling.
- A Billing Project for each **cohort**, if you would like to track spending per data set

If you are uncertain, **we recommend starting by setting up a Billing Project per lab member**.  This makes it easy to track lab member spending, and also makes it easier to cleanly shut down projects when a member leaves the lab.

#### Create a Billing Project

1. [Launch Terra](https://anvil.terra.bio/#workspaces) and sign in with your Google account.  **Make sure to use the same Google account that you used to set up Google Billing.**
    + If this is your first time logging in to Terra, you will need to accept the Terms of Service.
1. In the drop-down menu on the left, navigate to “Billing”.
    + Click the triple bar in the top left corner to access the menu.
    + Click the arrow next to your name to expand the menu.
    + Click Billing.
    +
```{r, echo=FALSE, fig.alt='Screenshot of the Terra drop-down menu.  Three items are highlighted: 1) the "hamburger" button for extending the drop-down menu, 2) the arrow next to your username, for extending the drop-down submenu, and 3) the submenu item "Billing".'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_222")
```

1. On the Billing page, click the **plus icon** to create a new Billing Project.
    + If prompted, select the Google account to use.  Make sure to use the same Google account that you used to set up Google Billing.
    + If prompted, give Terra permission to manage Google Cloud Platform billing accounts.
    +
```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing Page.  The "plus" button next to "Billing Projects" is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_226")
```

1. Enter a unique name for your Terra Billing Project and select the appropriate Google Billing Account.
    + The name of the Terra Billing Project must:
        + Only contain lowercase letters, numbers and hyphens
        + Start with a lowercase letter
        + Not end with a hyphen
        + Be between 6 and 30 characters
        + Be unique across all Google Billing Projects
    +
```{r, echo=FALSE, fig.alt='Screenshot of the Terra Add Billing Project dialog box.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_230")
```

As mentioned above, we recommend creating separate Terra Billing Projects for each of your team members so you can track their spending.  These Billing Projects can all be associated with the same Google Billing Account if they are all funded by the same source.

### Step 5: Set Budgets and Alerts

```{r, echo=FALSE, fig.alt="Diagram showing an overview of the six steps. Step 5 is highlighted."}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_0")
```

Cloud computing can save a great deal of money, time and effort by providing compute on an as-needed basis.  However, care must be taken that users do not accidentally request excessive resources, or leave resources running when not needed.

Unfortunately, there are two issues that make direct cost control difficult:

- **The Google Cloud billing interface does not provide a way to automatically cancel computations when a spending threshold is reached**
- **Compute costs are reported with a delay (~1 day)**

As a PI or lab manager, there are some steps you can take to help monitor and limit spending:

- Be careful with members and permissions in your Billing Projects and Workspaces on Terra (see [Adding Users and Workspaces](#step-6-add-users-and-workspaces) for recommended setup)
- Most importantly, **monitor your spending** so you can shut down unnecessary expensive activities before they have time to accumulate.
- Terra provides [extensive documentation and examples](https://support.terra.bio/hc/en-us/sections/360006459511-Controlling-Cloud-costs) regarding cost management while working in the cloud

**We highly recommended you set budgets and alerts to notify you if spending starts to exceed expectations**.  This will make it easier to notice and shut down any accidental overspending.  A good starting point is to set a monthly budget, and then set alerts at **50 percent** and **90 percent** of expected spend.  You can add additional alerts if you desire.

You can set a single Budget for your entire lab, set up individual budgets for each Billing Project, or even set budgets for certain subsets of your Billing Projects.  This will depend on the size of your lab and how closely you want to monitor spending.  More granular budgets make it quicker to notice and track down overspending from a particular project but mean you will get more emails every month.  When setting budgets with broader scope, you can always find out which particular Billing Project is spending the money by checking in the GCP Billing interface.  **NOTE: that there may be some restrictions on the budgets and alerts you can set while you’re using GCP’s free credits.**  At the time of writing (Feb 2021) you are not able to set budgets for individual projects while you are using the GCP free credits, but can still set an overall budget.  Any restrictions should be lifted when you upgrade to a paid account.

#### Set alerts

1. Log in to the [Google Cloud Platform](https://console.cloud.google.com/) console using your Google ID.
1. Navigate to [Billing](https://console.cloud.google.com/billing)
    +
    ```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console drop-down menu, with "Billing" highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_153")
```
    + You may be automatically directed to view a specific Billing Account.  If you see information about a single account (other than the one you're interested in), you can get back to the list of all your Billing Accounts by clicking "Manage Billing Accounts" from the drop-down menu.
    + 
```{r, echo=FALSE, fig.alt='Screenshot of an individual Google Cloud Billing Account with the drop-down menu item "Manage Billing Accounts" highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_167")
```

1. Click on the name of the Billing Account you want to set alerts for.
    +
```{r, echo=FALSE, fig.alt='Screenshot of Google Cloud Billing Accounts Overview. A Billing Account name is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_5")
```

1. In the left-hand menu, click "Budgets & alerts".
    + 
```{r, echo=FALSE, fig.alt='Screenshot of an individual Google Cloud Billing Account with the left-hand menu item "Budgets & alerts" highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_11")
```

1. Click "Create Budget".
    + 
```{r, echo=FALSE, fig.alt='Screenshot of the budgets and alerts page for a Google Cloud Billing Account. The "Create Budget" button highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_17")
```

1. Enter a name for your budget, and then choose what you want to monitor.  Click "Next".
    +
```{r, echo=FALSE, fig.alt='Screenshot of the form for setting budget scope for a Google Cloud Billing Account. Three things are highlighted:  1) the box for entering a "Name" for the budget, 2) the dropdown menu labeled "Projects" for selecting which Billing Projects are part of the budget, and 3) the "Next" button.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_24")
```


1. For Budget Type, select "Specified amount".  Enter the total budget amount for the month (you will set alerts at different thresholds in the next step).  Click "**Next**" (not "Finish").
    +
```{r, echo=FALSE, fig.alt='Screenshot of the form for setting budget amount for a Google Cloud Billing Account.  The drop-down menu labeled "Budget type" is highlighted and "Specified amount" is selected.  Also highlighted are the text box labeled "Target amount" and the "Next" button.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_32")
```


1. Enter the threshold amounts where you want to receive an alert.  We recommend starting with 50% and 90%.  You can set other alerts if you prefer.
    +
```{r, echo=FALSE, fig.alt='Screenshot of the form for setting budget actions for a Google Cloud Billing Account.  The boxes for entering "Percent of budget" or "Amount" are highlighted.  The drop-down menu labeled "Trigger on" is highlighted and "Actual" is selected.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_40")
```


1. Check the box for "Email alerts to billing admins and users".  Click "**Finish**".  Now you (as the owner and admin), along with anyone you added with admin or user privileges (e.g lab managers) will receive alerts when your lab members reach the specified spending thresholds.  These emails will be sent to the Gmail accounts associated with the Billing Account.
    +
```{r, echo=FALSE, fig.alt='Screenshot of the form for setting budget alerts for a Google Cloud Billing Account.  The checkbox labeled "Email alerts to billing admins and users" is highligheted and checked.  The "Finish" button is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_44")
```


1. You can edit your budgets at any time by going to Billing > Budgets & alerts, and clicking on the name of the budget you want to edit.
    +
```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Billing Account Budgets and alerts overview.  Four items are highlighted illustrating how to view and edit an existing budget: 1) The top-left "hamburger" button for extending the drop-down menu, 2) the drop-down menu item "Billing", 3) the submenu item "Budgets & alerts, 4) the name of a budget.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_55")
```



### Step 6: Add Users and Workspaces

```{r, echo=FALSE, fig.alt="Diagram showing an overview of the six steps. Step 6 is highlighted."}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_0")
```

Finally, back on Terra, you can add lab members and give them permission to run analyses funded through your Billing Projects.

There are two primary ways to permit users to charge to your Billing Projects:

- **Add them directly to the Billing Project**.  This gives them flexibility to create and manage their own Workspaces, but reduces your control over spending.   Anyone they add to their Workspaces with sufficient permissions (i.e. permission to compute) can charge to your Billing Project.
- **Create a Workspace yourself, and add them to the Workspace** (or have a designated Lab Manager responsible for managing Workspaces).  This gives you much more control over who can charge to your Billing Project.

Billing permissions on Terra can be confusing.  For this reason, **We recommend starting by having a single person responsible for managing all Workspaces (either yourself or a trusted "lab manager").  This person should create all Workspaces and add lab members as Writers (not Owners) to the Workspaces**.  This provides the greatest control over spending.  Once you are familiar with the permissions system and are certain your lab members understand the implication of different permission settings, you may decide to give them greater control over Workspace access.

#### Create a new Workspace

1. [Launch Terra](https://anvil.terra.bio/#workspaces)
1. In the drop-down menu on the left, navigate to "Workspaces".
    + Click the triple bar in the top left corner to access the menu.
    + Click "Workspaces".
    +
```{r, echo=FALSE, fig.alt='Screenshot of Terra drop-down menu.  The "hamburger" button to extend the drop-down menu is highlighted, and the menu item "Workspaces" is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_75")
```
1. Click on the **plus icon** near the top of left of the page.
    +
```{r, echo=FALSE, fig.alt='Screenshot of Terra Workspaces page.  The "+" is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_69")
```


1. Name your Workspace and select the appropriate Billing Project.  **All activity in the Workspace will be charged to this Billing Project** (regardless of who conducted it).
    +
```{r, echo=FALSE, fig.alt='Screenshot of Terra dialog box for creating a new Workspace.  The text box labeled "Workspace name" and the drop-down menu labeled "Billing project" are highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_84")
```

1. If you are working with protected data, you can set the **Authorization Domain** to limit who can be added to your Workspace.  Note that the Authorization Domain cannot be changed after the Workspace is created (i.e. there is no way to make this Workspace shareable with a larger audience in the future).  Workspaces by default are only visible to people you specifically share them with.  Authorization domains add an extra layer of enforcement over privacy, but by nature make sharing more complicated.  We recommend using Authorization Domains in cases where it is extremely important and/or legally required that the data be kept private (e.g. protected patient data, industry data).  For data you would merely prefer not be shared with the world, we recommend relying on standard Workspace sharing permissions rather than Authorization Domains, as Authorization Domains can make future collaborations, publications, or other sharing complicated.
    +
```{r, echo=FALSE, fig.alt='Screenshot of Terra dialog box for creating a new Workspace.  The drop-down menu labeled "Authorization domain" is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_91")
```

1. Click "Create Workspace".  The new workspace should now show up under your Workspaces.
    +
```{r, echo=FALSE, fig.alt='Screenshot of Terra dialog box for creating a new Workspace.  The "Create Workspace" button is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_97")
```

**To start, we recommend creating one Workspace for each lab member** (associated with that lab member’s Billing Project, if you have created separate Billing Projects for your lab members).  This will enable you and your lab members to familiarize yourself with Workspaces and decide how best to organize your work.  You can then create additional Workspaces as needed (there are no limits on the number of Workspaces).

#### Add members to Workspaces

Lab members must have logged in to Terra at least once before they can be added to your Billing Projects and Workspaces (they do not need to log in to Google Cloud Console).

1. [Launch Terra](https://anvil.terra.bio/#workspaces)
1. In the drop-down menu on the left, navigate to "Workspaces".
    + Click the triple bar in the top left corner to access the menu.
    + Click "Workspaces".
    +
```{r, echo=FALSE, fig.alt='Screenshot of Terra drop-down menu.  The "hamburger" button to extend the drop-down menu is highlighted, and the menu item "Workspaces" is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_75")
```

1. Click on the name of the Workspace to open the Workspace.
    + Opening a Workspace does not cost anything.  Certain activities in the Workspace (such as running an analysis) will charge to the Workspace’s Billing Project.  Workspace management (e.g. adding and removing members, editing the description) does not cost money.
    +
```{r, echo=FALSE, fig.alt='Screenshot of Terra Workspace page.  The name of a Workspace is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_103")
```

1. Click the circle with 3 dots on the right hand side to open the Workspace management menu.  Click "Share"
    +
```{r, echo=FALSE, fig.alt='Screenshot of an individual Terra Workspace dashboard page.  The button for extending the Workspaces\'s drop-down menu is highlighted, and the menu item "Share" is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_109")
```

1. Enter the email address of the user you want to share the Workspace with.  This must be the address associated with the account they are using to access Terra.
    +
```{r, echo=FALSE, fig.alt='Screenshot of the dialog box for sharing a Terra Workspace.  The text box labeled "User email" is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_116")
```

1. Choose their permission level.  **We recommend adding lab members as Writers** to start.  This gives them permission to freely use the Workspace, (adding and removing data, conducting analyses, etc.) but prevents them from adding additional members who could charge to your Billing Project.
    + "Can compute" should be checked
    + "Can share" should **NOT** be checked
    +
```{r, echo=FALSE, fig.alt='Screenshot of the dialog box for sharing a Terra Workspace.  The drop-down menu labeled with the email of the user you are sharing with is highlighted and the menu item "Writer" is selected.  The check box labeled "Can share" is annotated with the word "No" and is unchecked.  The checkbox labeled "Can compute" is annotated with the word "Yes" and is checked.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_128")
```

1. Click "Save".  The user should now be able to see the Workspace when logged in to Terra.
    +
```{r, echo=FALSE, fig.alt='Screenshot of the dialog box for sharing a Terra Workspace.  The "Save" button is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_132")
```

#### User access levels and permissions

Managing permissions for your Workspace has important implications:

- **Billing**: Terra charges are associated with Workspaces rather than users.  Any billable activity that takes place in a given Workspace will be charged to the associated Billing Project, regardless of who conducted the activity.  If there are multiple users with permission to compute, you won’t be able to tell who conducted the activity.
- **Data access**: Especially when working with protected data, it’s important to ensure that users have proper authorization to view the data before giving them access to a Workspace containing the data.  Terra provides **Authorization Domains** to assist with this.

In general we recommend:

- **Writers: Lab members who need permission to compute** (and charge to your Billing Project).
- **Readers: All other users** (i.e. users who need to see the Workspace but should not charge to your Billing Project).  Readers can always “clone” the Workspace (creating a copy of it associated with their own Billing Project) if they want to run computations themselves.
- If working with protected data, take advantage of Authorization Domains to increase security.

```{r, echo=FALSE, fig.alt='Table summarizing Workspace permission levels.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_122")
```

More details about the permissions associated with each Access Level can be found in the [Terra documentation](https://support.terra.bio/hc/en-us/articles/360025851892-Reader-writer-or-owner-Workspace-access-controls-explained).

### Wrap-Up

**Congratulations!  You have successfully set up AnVIL for your lab!**

Your lab members should be free to carry out analyses in the Workspaces you created.  You should not need to do any further configuration through Terra until you decide to add or change user permissions for your Billing Projects and Workspaces.

You can view costs at any time through [Google Cloud Billing](https://console.cloud.google.com/billing).  Note that costs are reported with a delay (~1 day).


## Budget Templates

If you want to apply for a grant and you plan to use the AnVIL platform for data storage, data movement, and data analysis, you can include the anticipated costs in your proposal. We have created a template for the budget justification paragraph of your grant proposal. The documents described in the following provide you with insightful knowledge.


### Types of Costs

There are three types of costs that are typically occur when performing operations on the Google Cloud Platform.

**1. Cost for Computing** is driven by your particular CPU and memory requirements. Importantly, you can save money if your work can tolerate being interrupted (also known as a preemptible compute resource). In this case, you pay less per hour with the understanding that your work may be interrupted by a customer willing to pay more. Details and current pricing can be found [here](https://cloud.google.com/compute/all-pricing#top_of_page).

**2. Cost for Storage** is driven by the amount of data and the length of time you wish to store the data. Here, you can save money if you have data that you do not plan to access frequently. This would be the case for raw data that has already been processed, backups, and archives. Details and current pricing can be found [here](https://cloud.google.com/storage/pricing#storage-pricing and https://cloud.google.com/compute/all-pricing#localssdpricing).

**3. Cost for Network Usage (egress)** applies to data being transferred out of a Cloud resource. In this context, a Cloud resource refers to a set of computers in a particular region. This would apply, for example, if you transferred data from Google’s East Coast computers to Amazon’s West Coast computers. In general, while it’s free to upload data to the Cloud, you will incur costs when downloading data to your local computer or between Cloud regions. Details and current pricing can be found [here](https://cloud.google.com/storage/pricing#network-egress).


### Usage of Budget Templates

In a first step, you can use the template Google Sheet [AnVIL_Cost_Estimator](https://docs.google.com/spreadsheets/d/1GUN93HDRqDbZ0uktaZjoP-y8Ril1T_VIJnQrjRD6tV4) to calculate costs for computing, storage, and network usage (egress) for your proposal. In a second step, you can use the template Google Doc [AnVIL_Budget_Justification](https://docs.google.com/document/d/145JFLn2hviLmaYF-mO06gbCkG0i4HRaWvkUBKORo85Y) to create a budget justification paragraph for your proposal by including the information highlighted in <span style="background-color: #EA33F7">pink</span>
 (mostly copying entries from your Google Sheet **AnVIL_Cost_Estimator**). Please download and adapt both documents to your project. 
 
Please check that the prices are up to date by using the links listed below or in the [AnVIL_Cost_Estimator](https://docs.google.com/spreadsheets/d/1GUN93HDRqDbZ0uktaZjoP-y8Ril1T_VIJnQrjRD6tV4).  

For further guidance, you can have a look at a completed document [AnVIL_Budget_Justification_Example](https://docs.google.com/document/d/1qMZNvZig7vNXposBxA77AIASY0gDCwaYwGl2YwzHXuY).

