# Data Analysts

This chapter is targeted towards people who are joining an existing team on AnVIL. You will find here:

- **Account Setup Overview** -- Introductory information and goals for this guide
- **Account Setup Steps** -- Step-by-step instructions to create your first accounts on AnVIL

## Account Setup Overview {#overview-analysts}

**Terra** is the compute engine of AnVIL; i.e. where you will run your analyses.  Terra currently offers access to **Jupyter Notebooks** and **RStudio** for interactive analysis, as well as the **Workflow Description Language** (WDL) for batch processing of many samples.  Behind the scenes, Terra runs on Google Cloud Platform, so you will need a (free) Google Account.

```{r, echo=FALSE, fig.alt='Diagram illustrating the relationship between Terra and Google Cloud Platform.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1tyt8ifxD3y7QW3nN27jh02aPrBvNEo1GN_u2Ne_UngM/edit#slide=id.gd84a304855_0_138")
```

1. Create a Google account
1. [Launch Terra](https://anvil.terra.bio/#workspaces) and sign in with your Google account
1. Link external accounts (Gen3, dbGaP) to Terra (optional - enables you to import AnVIL open access datasets and to access protected data if you have appropriate authorization)

## Step 1: Create a Google Account

Terra operates on Google Cloud Platform, so you will need a (free) Google account to create a Terra account and run analyses on AnVIL.

```{r, child=c("_child_create_google_account.Rmd")}

```

## Step 2: Set Up Terra

[Launch Terra](https://anvil.terra.bio/#workspaces), and you should be prompted to sign in with your Google account.

- Once you have signed in, your Terra account is set up and your PI or manager should be able to add you to projects.
- If this is the **first time you or your team has used Terra**, the PI will also need to set up billing.

You can always access Terra by going to [`anvil.terra.bio`](https://anvil.terra.bio/), or by clicking the link on the AnVIL home page.

```{r, echo=FALSE, fig.alt='Screenshot of the AnVIL home page. The button to "launch Terra" is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1tyt8ifxD3y7QW3nN27jh02aPrBvNEo1GN_u2Ne_UngM/edit#slide=id.gde7783227e_0_31")
```

## Step 3: Link External Accounts (optional)

AnVIL provides access to a wide selection of datasets, including controlled-access data.  Linking your accounts will enable you to import these data into Terra.

The following links will take you to the Terra documentation for setting up and linking external accounts.

- [Set up a Gen3 account](https://gen3.theanvil.io/login) - allows you to use the Gen3 data explorer to create artificial cohorts over AnVIL datasets that have been indexed by Gen3.
- [Link Gen3 and Terra accounts](https://support.terra.bio/hc/en-us/articles/360050390451) - allows you to analyze Gen3 data on Terra.
- [Link Terra and eRA Commons ID](https://support.terra.bio/hc/en-us/articles/360038086332-Linking-Terra-to-External-Servers) - To use controlled-access data on Terra, you will need to link your Terra user ID to your authorization account (such as a dbGaP account). Linking to external servers will allow Terra to automatically determine if you can access controlled datasets hosted in Terra (ex. TCGA, TOPMed, etc.) based on your approved dbGaP applications.

## Wrap-Up