# (PART\*) Working on AnVIL {-}

# Workspaces

Workspaces are the building blocks of projects in Terra. Inside a Workspace, you can run analyses, launch interactive tools like RStudio and Galaxy, store data, and share results. The video below gives a brief introduction to the parts of a Workspace.

<iframe src="https://drive.google.com/file/d/18WUmQfDnulHdaMlrH0Eh6kwIP3zTkaqp/preview" width="640" height="360" allow="autoplay"></iframe>

## Create a New Workspace

Creating a new Workspace from scratch allows you to fully customize the contents. The following steps show you how to create a Workspace so you can get started.

```{r, child=c("_child_create_workspace.Rmd")}

```

## Clone an Existing Workspace

Cloning an existing Workspace allows you to copy existing documentation, code, and/or data into your own experimental space. That following steps show you how to clone a Workspace that has already been developed by other AnVIL users. When cloning, AnVIL makes a copy of notebooks and code for you to modify. Data however, is linked back to the original Workspace through Data Tables, which saves space!

```{r, child=c("_child_clone_workspace.Rmd")}

```