# RStudio

One of the analysis platforms available on AnVIL is RStudio. This platform offers rich genomics support through [Bioconductor](https://anvilproject.org/learn/run-interactive-analyses/getting-started-with-bioconductor). This chapter focuses on launching and highlighting a few features for RStudio.

## RStudio: Video tutorial

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_video.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

## RStudio: Step-by-step guide

This step-by-step guide provides written instructions and screenshots for getting started with RStudio on AnVIL.


### Launch RStudio Cloud Environment

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_launch.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

### Tour RStudio

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_tour.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```


### Pause RStudio {#stopping}

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_pause.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

### Delete RStudio Cloud Environment

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_rstudio_delete.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```



```{r}
sessionInfo()
```
