# Galaxy

One of the analysis platforms available on AnVIL is Galaxy. This platform offers a [graphical interface for thousands of tools](https://anvilproject.org/learn/run-interactive-analyses/getting-started-with-galaxy). This chapter focuses on launching and highlighting a few features for Galaxy.

## Galaxy: Video tutorial

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_galaxy_video.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

## Galaxy: Step-by-step guide

This step-by-step guide provides written instructions and screenshots for getting started with Galaxy on AnVIL.


### Starting Galaxy

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_galaxy_start.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

### Navigating Galaxy

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_galaxy_navigate.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

### Deleting Galaxy environment

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_galaxy_delete.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
