1. [Launch Terra](https://anvil.terra.bio/#workspaces) and sign in with your Google account.  **Make sure to use the same Google account that you used to set up Google Billing.**
    + If this is your first time logging in to Terra, you will need to accept the Terms of Service.
1. In the drop-down menu on the left, navigate to "Billing".
    + Click the triple bar in the top left corner to access the menu.
    + Click the arrow next to your name to expand the menu.
    + Click Billing.  
    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra drop-down menu. Three items are highlighted: 1) the "hamburger" button for extending the drop-down menu, 2) the arrow next to your username, for extending the drop-down submenu, and 3) the submenu item "Billing".'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_80")
    ```

1. On the Billing page, click **+ CREATE** to create a new Billing Project.
    + If prompted, select the Google account to use.  Make sure to use the same Google account that you used to set up Google Billing.
    + If prompted, give Terra permission to manage Google Cloud Platform billing accounts.
    +
    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing Page.  The "plus Create" button next to "Billing Projects" is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_88")
    ```

1. Enter a unique name for your Terra Billing Project and select the appropriate Google Billing Account.
    + The name of the Terra Billing Project can only contain lowercase letters, numbers and hyphens.
    + If you will be teaching multiple iterations of the course, be sure to include information about the date in the Billing Project name.
    + Click "CREATE BILLING PROJECT". It will take several minutes before the Billing Project is ready for use.  
    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Add Billing Project dialog box.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_98")
    ```