1. Log in to the [Google Cloud Platform](https://console.cloud.google.com/) console using the Google ID associated with your Google Cloud projects.

1. Open the dropdown menu on the top left and click on [Billing](https://console.cloud.google.com/billing).

    ```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console drop-down menu, with "Billing" highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1GBYTx25VzBFh7kI_elgMC0fmOMm4YhcfW8wIJ1EkmKY/edit#slide=id.g115e284bdc2_0_144")
    ```

1. You may be automatically directed to view a specific Billing Account. If you see information about a single account (and it’s not the one you’re interested in), you can get back to the list of all your Billing Accounts by clicking "Manage Billing Accounts" from the drop-down menu.

    ```{r, echo=FALSE, fig.alt='Screenshot of an individual Google Cloud Billing Account with the drop-down menu item "Manage Billing Accounts" highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1GBYTx25VzBFh7kI_elgMC0fmOMm4YhcfW8wIJ1EkmKY/edit#slide=id.g115e284bdc2_0_295")
    ```

1. Click on the name of the Billing Account you want to set alerts for.

    ```{r, echo=FALSE, fig.alt='Screenshot of Google Cloud Billing Accounts Overview. A Billing Account name is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1GBYTx25VzBFh7kI_elgMC0fmOMm4YhcfW8wIJ1EkmKY/edit#slide=id.g115e284bdc2_0_150")
    ```

1. In the left-hand menu, click "Budgets & alerts".
 
    ```{r, echo=FALSE, fig.alt='Screenshot of an individual Google Cloud Billing Account with the left-hand menu item "Budgets & alerts" highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1GBYTx25VzBFh7kI_elgMC0fmOMm4YhcfW8wIJ1EkmKY/edit#slide=id.g115e284bdc2_0_442")
    ```

1. Click the "Create Budget" tab.

    ```{r, echo=FALSE, fig.alt='Screenshot of the budgets and alerts page for a Google Cloud Billing Account. The "Create Budget" button highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1GBYTx25VzBFh7kI_elgMC0fmOMm4YhcfW8wIJ1EkmKY/edit#slide=id.g115e284bdc2_0_587")
    ```

1. Enter a name for your budget, and then choose which projects you want to monitor. Then click "Next".

    ```{r, echo=FALSE, fig.alt='Screenshot of the form for setting budget scope for a Google Cloud Billing Account. Three things are highlighted:  1) the box for entering a "Name" for the budget, 2) the dropdown menu labeled "Projects" for selecting which Billing Projects are part of the budget, and 3) the "Next" button.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1GBYTx25VzBFh7kI_elgMC0fmOMm4YhcfW8wIJ1EkmKY/edit#slide=id.g115e284bdc2_0_732")
    ```

1. For Budget Type, select "Specified amount". Enter the total budget amount for the month (you will set alerts at different thresholds in the next step). Click "**Next**" (do not click "Finish").

    ```{r, echo=FALSE, fig.alt='Screenshot of the form for setting budget amount for a Google Cloud Billing Account.  The drop-down menu labeled "Budget type" is highlighted and "Specified amount" is selected.  Also highlighted are the text box labeled "Target amount" and the "Next" button.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1GBYTx25VzBFh7kI_elgMC0fmOMm4YhcfW8wIJ1EkmKY/edit#slide=id.g115e284bdc2_0_878")
    ```

1. Enter the threshold amounts where you want to receive an alert. We recommend starting with 50% and 90%. You can set other alerts if you prefer.

    ```{r, echo=FALSE, fig.alt='Screenshot of the form for setting budget actions for a Google Cloud Billing Account.  The boxes for entering "Percent of budget" or "Amount" are highlighted.  The drop-down menu labeled "Trigger on" is highlighted and "Actual" is selected.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1GBYTx25VzBFh7kI_elgMC0fmOMm4YhcfW8wIJ1EkmKY/edit#slide=id.g115e284bdc2_0_1025")
    ```

1. Check the box for "Email alerts to billing admins and users", then click "**Finish**". Now you (as the owner and admin), along with anyone you added with admin or user privileges (e.g. lab managers) will receive alerts when your lab members reach the specified spending thresholds. These emails will be sent to the Gmail accounts associated with the Billing Account.

    ```{r, echo=FALSE, fig.alt='Screenshot of the form for setting budget alerts for a Google Cloud Billing Account.  The checkbox labeled "Email alerts to billing admins and users" is highligheted and checked.  The "Finish" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1GBYTx25VzBFh7kI_elgMC0fmOMm4YhcfW8wIJ1EkmKY/edit#slide=id.g115e284bdc2_0_1169")
    ```

1. You can edit your budgets at any time by going to Billing > Budgets & alerts, and clicking on the name of the budget you want to edit.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Billing Account Budgets and alerts overview.  Four items are highlighted illustrating how to view and edit an existing budget: 1) The top-left "hamburger" button for extending the drop-down menu, 2) the drop-down menu item "Billing", 3) the submenu item "Budgets & alerts, 4) the name of a budget.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1GBYTx25VzBFh7kI_elgMC0fmOMm4YhcfW8wIJ1EkmKY/edit#slide=id.g115e284bdc2_0_1314")
    ```

