You can always check your current spend through the Google Billing console, but remember

- There is a reporting delay (~1 day), so you cannot immediately see what an analysis cost
- Costs are reported at the level of Billing Projects, so if you have not created separate Billing Projects, you will not be able to determine where charges are coming from.

The Google Billing console displays information by Billing Account.  To view spending:
  
  1. Log in to the [Google Cloud Platform](https://console.cloud.google.com/) console using your Google ID.
1. Navigate to [Billing](https://console.cloud.google.com/billing)
+
  ```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console drop-down menu, with "Billing" highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_153")
```
+ You may be automatically directed to view a specific Billing Account.  If you see information about a single account (other than the one you're interested in), you can get back to the list of all your Billing Accounts by clicking "Manage Billing Accounts" from the drop-down menu.
    + 
```{r, echo=FALSE, fig.alt='Screenshot of an individual Google Cloud Billing Account with the drop-down menu item "Manage Billing Accounts" highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gd84a304855_0_167")
```

1. Click on the name of the Billing Account for the project you want to view.
    +
```{r, echo=FALSE, fig.alt='Screenshot of Google Cloud Billing Accounts Overview. A Billing Account name is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.gda79c11827_0_5")
```

1. The top of the Overview tab shows your month-to-date spending
![]()
    +
```{r, echo=FALSE, fig.alt='Screenshot of a Google Cloud Billing Account Overview.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.ge3b5f92447_0_0")
```

1. Scroll further down on the Overview screen to show your top projects.
    +
```{r, echo=FALSE, fig.alt='Screenshot of a Google Cloud Billing Account top projects.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.ge3b5f92447_0_4")
```

1. The **Reports** tab is probably the most useful screen for diving down and exploring costs of individual projects over time.
    +
```{r, echo=FALSE, fig.alt='Screenshot of a Google Cloud Billing Account Reports tab.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.ge3b5f92447_0_8")
```

1. The **Cost table** tab provides a convenient table of spending per project.
    +
```{r, echo=FALSE, fig.alt='Screenshot of a Google Cloud Billing Account Cost table tab.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/162GS7ArBPM4w_rPazcUrpnoEKT7jx9i7fpPQkH_iC_0/edit#slide=id.ge3b5f92447_0_12")
```
