1. [Launch Terra](https://anvil.terra.bio/#workspaces) and sign in with your Google account.  **Make sure to use the same Google account that you used to set up Google Billing.** If this is your first time logging in to Terra, you will need to accept the Terms of Service.

1. In the drop-down menu on the left, navigate to "Billing". Click the triple bar in the top left corner to access the menu. Click the arrow next to your name to expand the menu, then click "Billing".

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra drop-down menu.  Three items are highlighted: 1) the "hamburger" button for extending the drop-down menu, 2) the arrow next to your username, for extending the drop-down submenu, and 3) the submenu item "Billing".'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1POwxqv4p6AfPHJlN9VNq0TaT44fA2RAFSpIERIMHdWU/edit#slide=id.g116f8d759be_0_2")
    ```

1. On the Billing page, click the "+ CREATE" button to create a new Billing Project. If prompted, select the Google account to use.  Make sure to use the same Google account that you used to set up Google Billing. If prompted, give Terra permission to manage Google Cloud Platform billing accounts.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing Page.  The "plus" button next to "Billing Projects" is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1POwxqv4p6AfPHJlN9VNq0TaT44fA2RAFSpIERIMHdWU/edit#slide=id.g116f8d759be_0_149")
    ```

1. Enter a unique name for your Terra Billing Project and select the appropriate Google Billing Account. The name of the Terra Billing Project must:
    + Only contain lowercase letters, numbers and hyphens
    + Start with a lowercase letter
    + Not end with a hyphen
    + Be between 6 and 30 characters
    + Be unique across all Google Billing Projects

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Add Billing Project dialog box.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1POwxqv4p6AfPHJlN9VNq0TaT44fA2RAFSpIERIMHdWU/edit#slide=id.g116f8d759be_0_293")
    ```

The page doesn't always update as soon as the billing project is created.  If it's been a couple of minutes and you don't see a change, try refreshing the page.
