1. Log in to the [Google Cloud Platform](https://console.cloud.google.com/) console using your Google ID. **Make sure to use the same Google account ID you use to log into Terra.**  

1. If you are a first time user, don’t forget to claim your free credits! If you haven't been to the console before, once you accept the Terms of Service you will be greeted with an invitation to "Try for Free."

    ```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console with the "Try for Free" button highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1tGpzZaQxoTAcxs_nyyNL2FOqypjEofEnMVpBtZiAw4A/edit#slide=id.g116ca06e27d_0_0")
    ```

1. Follow the instructions to sign up for a Billing Account and get your credits. 

1. Choose “Individual Account”. This “billing account” is just for managing billing, so you don’t need to be able to add your lab members. You will need to give either a credit card or bank account for security. Don't worry! **You won't be billed until you explicitly turn on automatic billing**.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Billing Account Setup, with "Individual Account" highlighted.  Also highlighted is text stating "You won\'t be charged unless you manually upgrade to a paid account."'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1tGpzZaQxoTAcxs_nyyNL2FOqypjEofEnMVpBtZiAw4A/edit#slide=id.g116ca06e27d_0_146")
    ```

1. You can view and edit your new Billing Account, by selecting “Billing” from the left-hand menu, or going direction to the billing console [console.cloud.google.com/billing](https://console.cloud.google.com/billing) 

    ```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console dropdown menu, with "Billing" highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1tGpzZaQxoTAcxs_nyyNL2FOqypjEofEnMVpBtZiAw4A/edit#slide=id.g116ca06e27d_0_293")
    ```

1. Clicking on the Billing Account name will allow you to manage the account, including accessing reports, setting alerts, and managing payments and billing.  We will cover account management in greater detail below.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console Billing Page, with the name of the new billing account highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1tGpzZaQxoTAcxs_nyyNL2FOqypjEofEnMVpBtZiAw4A/edit#slide=id.g116ca06e27d_0_437")
    ```

At any point, you can create additional Billing Accounts using the **Create Account** button.  We recommend creating a new Billing Account for each funding source.
