Anyone you wish to add to the Billing Account will need their own Google ID.

To add a member to a Billing Project:
  
1. Log in to the [Google Cloud Platform](https://console.cloud.google.com/) console using your Google ID.
1. Navigate to [Billing](https://console.cloud.google.com/billing)

    ```{r, echo=FALSE, fig.alt='Screenshot of the Google Cloud Console drop-down menu, with "Billing" highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1j1wRbaDyHJJhZQcWcP4xeYgIoaIBRIF3LIZpiDPBumw/edit#slide=id.g115e284bdc2_0_144")
    ```

1. You may be automatically directed to view a specific Billing Account.  If you see information about a single account rather than a list of your Billing Accounts, you can get back to the list by clicking "Manage Billing Accounts" from the drop-down menu.

    ```{r, echo=FALSE, fig.alt='Screenshot of an individual Google Cloud Billing Account with the drop-down menu item "Manage Billing Accounts" highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1j1wRbaDyHJJhZQcWcP4xeYgIoaIBRIF3LIZpiDPBumw/edit#slide=id.g115e284bdc2_0_295")
    ```

1. Check the box next to the Billing Account you wish to add a member to, click "ADD MEMBER".

    ```{r, echo=FALSE, fig.alt='Screenshot of Google Cloud Billing Accounts Overview. The checkbox next to the name of a Billing Account is checked and highlighted, and the "Add Member" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1j1wRbaDyHJJhZQcWcP4xeYgIoaIBRIF3LIZpiDPBumw/edit#slide=id.g116e2c647a7_0_151")
    ```

1. Enter their Google ID in the text box. In the drop-down menu, mouse over Billing, then choose the appropriate role.

    ```{r, echo=FALSE, fig.alt='Screenshot of the dialogue box for adding a member to a Google Cloud Billing Accounts. In the drop-down menu labeled "Select a Role", the item "Billing" and the submenu item "Billing Account Viewer" are highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1j1wRbaDyHJJhZQcWcP4xeYgIoaIBRIF3LIZpiDPBumw/edit#slide=id.g116e2c647a7_0_296")
    ```

1. Click "SAVE".

    ```{r, echo=FALSE, fig.alt='Screenshot of the dialogue box for adding a member to a Google Cloud Billing Accounts. The Save button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1j1wRbaDyHJJhZQcWcP4xeYgIoaIBRIF3LIZpiDPBumw/edit#slide=id.g116e2c647a7_0_441")
    ```
