1. [Launch Terra](https://anvil.terra.bio/#workspaces) and sign in with your Google account.  **Make sure to use the same Google account that you used to set up Google Billing.**

1. In the drop-down menu on the left, navigate to "Groups".
    + Click the triple bar in the top left corner to access the menu.
    + Click the arrow next to your name to expand the menu.
    + Click "Groups".  
    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra drop-down menu.  Three items are highlighted: 1) the "hamburger" button for extending the drop-down menu, 2) the arrow next to your username, for extending the drop-down submenu, and 3) the submenu item "Groups".'}
    leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdd7e85f9a2_0_17")
    ```

1. Create a New Group
    + On the Groups page, click the **plus icon** to create a new Group.  
    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Groups Page.  The "plus" button next to "Create a New Group" is highlighted.'}
    leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_6")
    ```

1. Enter a unique name for your Group.
    + The name of the Group can only contain letters, numbers, underscores, and dashes. Use an easy-to-search Group name (such as institution-course)
    + Keep the "Allow anyone to request access" option selected.
    + Click "CREATE GROUP".  
    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Create New Group dialog box.'}
    leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_16")
    ```

1. Find your new Group
    + Your new Group will appear on the [Groups](https://anvil.terra.bio/#groups) page. Note that if you have many groups you can also use the search box.
    + Note the `firecloud.org` address associated with your Group.  
    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Groups page. The new Group now appears. The Group firecloud.org address "JHU-bioinformatics-intro-workshop@firecloud.org" is highlighted.'}
    leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_24")
    ```
    + Click on the Group name.  
    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Groups page. The Group name is highlighted and should be clicked in order to add users.'}
    leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_32")
    ```
                                             
1. Add students to your Group
    + On the Group Management page, click the **plus icon** to "Add a User".  
    ```{r, echo=FALSE, fig.alt='Screenshot of the Group Management page. The "plus" button next to "Add a User" is highlighted.'}
    leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_38")
    ```
    + Enter the first participant's/student's Gmail account, leaving the "Can manage users (admin)" box **unchecked**.
    + Click "ADD USER".  
    ```{r, echo=FALSE, fig.alt='Screenshot of the "Add a User" dialog box. The student email is filled in for User email. The "Can manage users (admin)" box is unchecked. The ADD USER button is highlighted.'}
    leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_47")
    ```
    + Repeat the above steps to add additional participants.
                                             
1. Add a Teaching Assistant or additional instructor (optional)
    + On the Group Management page, click the **plus icon** to "Add a User".  
    ```{r, echo=FALSE, fig.alt='Screenshot of the Group Management page. The "plus" button next to "Add a User" is highlighted.'}
    leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_38")
    ```
    + Enter the Teaching Assistant's Gmail account.
    + Check the "Can manage users (admin)" box.
    + Click "ADD USER".  
    ```{r, echo=FALSE, fig.alt='Screenshot of the "Add a User" dialog box. The Teaching Assistant email is filled in for User email. The "Can manage users (admin)" box is checked. The ADD USER button is highlighted.'}
    leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_54")
    ```