---
title: "Getting Started on AnVIL"
date: "`r format(Sys.time(), '%B %d, %Y')`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Guides to help new AnVIL users set up their accounts and start doing research on the AnVIL platform"
favicon: assets/AnVIL_style/anvil_favicon.ico
---

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), "bookdown", "knitr", "rmarkdown"
), "packages.bib")
```

# About this Book {-}

This book is part of a series of books for the Genomic Data Science Analysis, Visualization, and Informatics Lab-space (AnVIL) of the National Human Genome Research Institute (NHGRI). Here, we present opinionated step-by-step guides for setting up accounts focused on three personas: PIs, Analysts, and Consortia.

```{r, echo=FALSE, fig.align='center', fig.alt= "Icons representing PIs, Analysts, and Consortia personas.", out.width = '80%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1kGxHkP0JVPNF1kla5XEqaIt1yz9s4ZbgzJ2zfL7GmTE/edit#slide=id.gf8e59f4b48_0_0")
```

### Skills Level {-} 

Please choose the closest matching persona from the lefthand menu.

::: {.notice}
_Genetics_

**Novice**: no genetics knowledge needed

_Programming skills_

**Novice**: no programming experience needed
:::

### AnVIL Collection {-}

Additional guides are provided to help you with Workspaces, launch interactive tools, and start working with data. Learn more about AnVIL by visiting https://anvilproject.org or reading the [article in Cell Genomics](https://www.sciencedirect.com/science/article/pii/S2666979X21001063).

Please check out our full collection of AnVIL and related resources: https://hutchdatascience.org/AnVIL_Collection/
