---
title: "Getting Started on AnVIL"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Guides to help new AnVIL users set up their accounts and start doing research on the AnVIL platform"
---

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), "bookdown", "knitr", "rmarkdown"
), "packages.bib")
```

# About this Book {-}

This book is part of a series of books for the NHGRI’s Genomic Data Science Analysis, Visualization, and Informatics Lab-space (AnVIL).  Here, we present opinionated step-by-step guides for setting up accounts focused on three personas: PIs, Analysts, and Consortia.

```{r, echo=FALSE}
leanbuild::include_slide("https://docs.google.com/presentation/d/18yUr5XSEMgPk8JXFLKfG9JF7L9NpKbCF_mIcXagogKg/edit#slide=id.gf8e59f4b48_0_0")
```

Additional guides are provided to help you with Workspaces, launch interactive tools, and start working with data.  Learn more about AnVIL by visiting https://anvilproject.org or reading the [preprint](https://www.biorxiv.org/content/10.1101/2021.04.22.436044v1).

Other books in this series include:

- [Using AnVIL in the Classroom](https://jhudatascience.org/AnVIL_Book_Teacher_Guide)
- Analysis Exercises Using AnVIL
- Galaxy on AnVIL
